---
title: "WHO coeficients for weight Z-score calculations"
author: "DS 150"
date: "2023-11-05"
categories: [health, child]
description: "See https://www.cdc.gov/nchs/data/nhsr/nhsr063.pdf for a desciption on how calculations are made.  However, the CDC has different coefficients."
params: 
    source: "https://github.com/hafen/growthstandards"
    pins_name: 'hathawayj/weight_coef'
    available: all
---


```{r}
#| echo: false
title <- params$title
description <- params$description
source <- params$source
pins_url <- params$pins_url
```

# `r params$title`

`r params$description`

```{python}
#| tags: [parameters]
#| echo: false
title = r.title
description = r.description
source = r.source
pins_url = r.pins_url

```


## Data details

```{r}
#| echo: false
#| warning: false
# https://aeturrell.github.io/skimpy/ python skimr for Python
library(pins)
library(tidyverse)
library(skimr)
library(arrow)
board <- board_connect()
dat <- pin_read(board, params$pins_name)
meta <- pin_meta(board, params$pins_name)
```

There are __`r prettyNum(nrow(dat), big.mark = ",", scientific = FALSE)` rows__ and __`r ncol(dat)` columns__. The data source[^1] is used to create our data that is stored in our [pins table](`r meta$local$url`). You can access this pin from a connection to [posit.byui.edu](https://posit.byui.edu) using ``r params$pins_name``.

This data is available to __`r params$available`__.

### Variable description

- __agedays:__ Age of child in days
- __sex:__ The gender of the child
- __mean:__ The mean for a child at agedays
- __cv:__ The [coefficient of variation](https://en.wikipedia.org/wiki/Coefficient_of_variation) for children at age in days
- __l:__ The box-cox transformation for children at age in days [see documentation](https://www.cdc.gov/nchs/data/nhsr/nhsr063.pdf)
- __sd:__ The standard deviation of weights for children at age age in days

### Variable summary

```{r}
#| echo: false
#| warning: false
skim(dat) |> yank("numeric")
```


```{r}
#| echo: false
#| warning: false
skim(dat) |> yank("character")
```

```{r}
#| echo: true
#| eval: false
#| code-fold: true
#| code-summary: Explore generating code using R
#| code-line-numbers: true
#| file: ../../../data_scripts/childheath/weight_coef.r
```

<!-- ```{python}
#| echo: true
#| eval: false
#| code-fold: true
#| code-summary: Explore generating code using Python
#| code-line-numbers: true
# file: ../../../data_scripts/childhealth.py
``` -->

[^1]: [`r params$source`](`r params$source`)