---
title: "Protein Requirement Campbell"
author: "MATH 221"
date: "2024-05-01"
categories: [MATH221, health, biology, nutrition]
description: "The protein requirement of an individual is the amount of protein they must consume daily to stay in equilibrium. This number varies from individual to individual. Nutritionists often give the protein requirement in terms of grams of good quality protein per kilogram of body weight per day (g P * kg-1 * d-1).\nIt is very difficult and expensive to measure the protein requirement in humans, but research into this area is very important. For example, how much protein should you give to a patient in a health care facility who must be fed enterally (i.e., through a feeding tube)? There are several ways in which nutritionists have tried to measure the protein requirement. Traditionally, they have used a method called Nitrogen Balance.\nIn a nitrogen balance experiment, researchers provide a carefully controlled diet containing prescribed amounts of protein to each subject for an extended period of time.  They then collect data on the amount of protein utilized by the body. This includes collecting and analyzing samples of urine, feces, blood, sweat, tears, exfoliated skin, etc.  Most researchers collect urine and fecal samples and estimate other losses. The protein requirement is estimated as the level of intake required so that the amount of protein consumed is exactly equal to the losses. Because of the difficulty of measuring protein losses, and since protein is essentially the only source for dietary nitrogen, nitrogen is used as a marker for protein.\nA nitrogen balance experiment was conducted to determine if there is a difference in the mean protein requirement of individuals in four groups: \n1. Old men (age 63-81)\n2. Old women (age 63-81)\n3. Young men (age 21-46)\n4. Young women (age 21-46)\nSubjects were provided with a controlled diet for three months and were required to comply with study protocol. The data set gives the measured protein requirements for each of the subjects. "
params: 
    source: "Wayne W. Campbell, Craig A. Johnson, George P. McCabe, and Nadine S. Carnell. Dietary protein requirements of younger and older adults. American Journal of Clinical Nutrition, 88(5):1322-1329, 2008. "
    pins_name: 'hathawayj/protein_requirement_campbell'
    available: all
---


```{r}
#| echo: false
title <- params$title
description <- params$description
source <- params$source
pins_url <- params$pins_url
```

# `r params$title`

`r params$description`

```{python}
#| tags: [parameters]
#| echo: false
title = r.title
description = r.description
source = r.source
pins_url = r.pins_url

```


## Data details

```{r}
#| echo: false
#| warning: false
# https://aeturrell.github.io/skimpy/ python skimr for Python
library(pins)
library(tidyverse)
library(skimr)
library(arrow)
board <- board_connect()
dat <- pin_read(board, params$pins_name)
meta <- pin_meta(board, params$pins_name)
url_path <- meta$local$url
file_name <- meta$file
object_name <- rev(unlist(str_split(meta$name, "/")))[[1]]
url_download <- paste0(
    str_remove(
        url_path,
        paste0(
            rev(unlist(str_split(url_path, "/")))[2],
            "/")),
    file_name)
```

There are __`r prettyNum(nrow(dat), big.mark = ",", scientific = FALSE)` rows__ and __`r ncol(dat)` columns__. The data source[^1] is used to create our data that is stored in our [pins table](`r meta$local$url`). You can access this pin from a connection to [posit.byui.edu](https://posit.byui.edu) using ``r params$pins_name``.

This data is available to __`r params$available`__.

### Variable description

- __Group:__ Group number (1 = elderly male, 2 = elderly woman, 3 = young male, 4 = young female)
- __Gender:__ Gender (Female, Male)
- __Age:__ Age (Elderly, Young)
- __ProteinRequirement:__ The protein requirement determined from the experiment in grams of protein per kilogram of body weight per day


### Variable summary

```{r}
#| echo: false
#| warning: false
skim(dat) |> yank("numeric")
```


```{r}
#| echo: false
#| warning: false
skim(dat) |> yank("character")
```

```{r}
#| echo: true
#| eval: false
#| code-fold: true
#| code-summary: Explore generating code using R
#| code-line-numbers: true
#| file: ../../../data_scripts/protein_requirement_campbell.R
```

<!-- ```{python}
#| echo: true
#| eval: false
#| code-fold: true
#| code-summary: Explore generating code using Python
#| code-line-numbers: true
#| file: ../../../data_scripts/YOURFILEPATH
``` -->


## Access data

This data is available to __`r params$available`__.

__Direct Download:__ [`r file_name`](`r url_download`)

#### __R and Python Download:__

##### __URL Connections:__

For public data, any user can connect and read the data using `pins::board_connect_url()` in R.

```r
library(pins)
url_data <- "https://posit.byui.edu/data/`r object_name`/"
board_url <- board_connect_url(c("dat" = url_data))
dat <- pin_read(board_url, "dat")
```

Use this custom function in Python to have the data in a Pandas DataFrame.

```python
import pandas as pd
import requests
from io import BytesIO

def read_url_pin(name):
  url = "https://posit.byui.edu/data/" + name + "/" + name + ".parquet"
  response = requests.get(url)
  if response.status_code == 200:
    parquet_content = BytesIO(response.content)
    pandas_dataframe = pd.read_parquet(parquet_content)
    return pandas_dataframe
  else:
    print(f"Failed to retrieve data. Status code: {response.status_code}")
    return None

# Example usage:
pandas_df = read_url_pin("`r object_name`")
```

#### __Authenticated Connection:__

Our connect server is [https://posit.byui.edu](https://posit.byui.edu/connect/#/content/listing?filter=min_role:viewer&filter=content_type:all&view_type=compact) which you assign to your `CONNECT_SERVER` environment variable. You must [create an API key](https://docs.posit.co/connect/user/api-keys/#api-keys-creating) and store it in your environment under `CONNECT_API_KEY`. 

_Read more about [environment variables and the pins package](../../environment.qmd) to understand how these environment variables are stored and accessed in R and Python with pins._

```r
library(pins)
board <- board_connect(auth = "auto")
dat <- pin_read(board, "`r params$pins_name`")
```


```python
import os
from pins import board_rsconnect
from dotenv import load_dotenv
load_dotenv()
API_KEY = os.getenv('CONNECT_API_KEY')
SERVER = os.getenv('CONNECT_SERVER')

board = board_rsconnect(server_url=SERVER, api_key=API_KEY)
dat = board.pin_read("`r params$pins_name`")
```

[^1]: [`r params$source`](`r params$source`)