---
title: "Comet Water Production and Magnitude"
author: "MATH 221"
date: "2024-04-26"
categories: [MATH221, astronomy, physics, science]
description: "A comet is a small icy object which orbits the sun.  As a comet approaches the sun, water and other particles thaw and detach from the comet.  This forms a small temporary atmosphere called a coma, and in some cases, a tail.\nWaterProduction is a measure of the amount of water that the comet is releasing. It is measured in terms of Log[Q(H2O)].  Higher values indicate that more water is being released.\nThe \"Magnitude\" of a comet is a measure of how bright it is appears to be.  The magnitude depends on several factors, including the distance to the comet.  The magnitude reported here is the negative of the \"heliocentric\" magnitude, or the magnitude of the comet as viewed 
from the location of the Sun.  Magnitude is measured as the negative logarithm of brightness. The AdjustedMagnitude is the negative of the magnitude, so brighter comets have higher positive values.\nImportant Note: Magnitude is measured on a negative logarithmic scale! This means that comets that are very bright have a low value for their magnitude. Faint comets have a high magnitude value.\nThe magnitude data have been adjusted by recording the negative of the magnitude.  "
params: 
    source: "L. Jorda, J. Crovisier, and D. W. E. Green. The correlation between water production rates and visual magnitudes in comets. Asteroids, Comets, Meteors 1991, 285-288, Houston, Texas, 1992. Lunar and Planetary Institute. "
    pins_name: 'hathawayj/comet_water_production_magnitude'
    available: all
---


```{r}
#| echo: false
title <- params$title
description <- params$description
source <- params$source
pins_url <- params$pins_url
```

# `r params$title`

`r params$description`

```{python}
#| tags: [parameters]
#| echo: false
title = r.title
description = r.description
source = r.source
pins_url = r.pins_url

```


## Data details

```{r}
#| echo: false
#| warning: false
# https://aeturrell.github.io/skimpy/ python skimr for Python
library(pins)
library(tidyverse)
library(skimr)
library(arrow)
board <- board_connect()
dat <- pin_read(board, params$pins_name)
meta <- pin_meta(board, params$pins_name)
url_path <- meta$local$url
file_name <- meta$file
object_name <- rev(unlist(str_split(meta$name, "/")))[[1]]
url_download <- paste0(
    str_remove(
        url_path,
        paste0(
            rev(unlist(str_split(url_path, "/")))[2],
            "/")),
    file_name)
```

There are __`r prettyNum(nrow(dat), big.mark = ",", scientific = FALSE)` rows__ and __`r ncol(dat)` columns__. The data source[^1] is used to create our data that is stored in our [pins table](`r meta$local$url`). You can access this pin from a connection to [posit.byui.edu](https://posit.byui.edu) using ``r params$pins_name``.

This data is available to __`r params$available`__.

### Variable description

- __AdjustedMagnitude:__ Brightness that a comet emits when placed one astronomical unit from Earth. Low magnitudes indicate brighter objects, and high magnitudes indicate more dim objects. The scale of magnitude is logarithmic. 
- __WaterProduction:__ The rate at which water vapor is released into space in Log[Q(H2O)]. Higher values indicate that more water is being released. 

### Variable summary

```{r}
#| echo: false
#| warning: false
skim(dat) |> yank("numeric")
```


```{r}
#| echo: false
#| warning: false
skim(dat) |> yank("character")
```

```{r}
#| echo: true
#| eval: false
#| code-fold: true
#| code-summary: Explore generating code using R
#| code-line-numbers: true
#| file: ../../../data_scripts/comet_water_production_magnitude.R
```

<!-- ```{python}
#| echo: true
#| eval: false
#| code-fold: true
#| code-summary: Explore generating code using Python
#| code-line-numbers: true
#| file: ../../../data_scripts/YOURFILEPATH
``` -->


## Access data

This data is available to __`r params$available`__.

__Direct Download:__ [`r file_name`](`r url_download`)

#### __R and Python Download:__

##### __URL Connections:__

For public data, any user can connect and read the data using `pins::board_connect_url()` in R.

```r
library(pins)
url_data <- "https://posit.byui.edu/data/`r object_name`/"
board_url <- board_connect_url(c("dat" = url_data))
dat <- pin_read(board_url, "dat")
```

Use this custom function in Python to have the data in a Pandas DataFrame.

```python
import pandas as pd
import requests
from io import BytesIO

def read_url_pin(name):
  url = "https://posit.byui.edu/data/" + name + "/" + name + ".parquet"
  response = requests.get(url)
  if response.status_code == 200:
    parquet_content = BytesIO(response.content)
    pandas_dataframe = pd.read_parquet(parquet_content)
    return pandas_dataframe
  else:
    print(f"Failed to retrieve data. Status code: {response.status_code}")
    return None

# Example usage:
pandas_df = read_url_pin("`r object_name`")
```

#### __Authenticated Connection:__

Our connect server is [https://posit.byui.edu](https://posit.byui.edu/connect/#/content/listing?filter=min_role:viewer&filter=content_type:all&view_type=compact) which you assign to your `CONNECT_SERVER` environment variable. You must [create an API key](https://docs.posit.co/connect/user/api-keys/#api-keys-creating) and store it in your environment under `CONNECT_API_KEY`. 

_Read more about [environment variables and the pins package](../../environment.qmd) to understand how these environment variables are stored and accessed in R and Python with pins._

```r
library(pins)
board <- board_connect(auth = "auto")
dat <- pin_read(board, "`r params$pins_name`")
```


```python
import os
from pins import board_rsconnect
from dotenv import load_dotenv
load_dotenv()
API_KEY = os.getenv('CONNECT_API_KEY')
SERVER = os.getenv('CONNECT_SERVER')

board = board_rsconnect(server_url=SERVER, api_key=API_KEY)
dat = board.pin_read("`r params$pins_name`")
```

[^1]: [`r params$source`](`r params$source`)