---
title: "Conjugated Linoleic Acid"
author: "MATH 221"
date: "2024-04-26"
categories: [MATH221, health, animals, nutrition]
description: "Conjugated linoleic acid (CLA) is found in milk fat from cows.  It has recently been discovered that CLA has several health-promoting characteristics, including cancer risk reduction.  The principal chemical form in which CLA is found in the milk fat is the “cis-9, trans-11” CLA.  Researchers in Alberta, Canada wanted to know if supplementing the diet of cattle with monensin, safflower oil, or both would affect the amount of CLA in the milk fat (measured in percent). Seven cattle were randomly assigned to each diet (including a control group)."
params: 
    source: "J. A. Bell, J. M. Griinari, and J. J. Kennelly. Effect of safflower oil, flaxseed oil, monensin, and vitamin E on concentration of conjugated linoleic acid in bovine milk fat. Journal of Dairy Science, 89:733-748, 2006. "
    pins_name: 'hathawayj/conjugated_linoleic_acid'
    available: all
---


```{r}
#| echo: false
title <- params$title
description <- params$description
source <- params$source
pins_url <- params$pins_url
```

# `r params$title`

`r params$description`

```{python}
#| tags: [parameters]
#| echo: false
title = r.title
description = r.description
source = r.source
pins_url = r.pins_url

```


## Data details

```{r}
#| echo: false
#| warning: false
# https://aeturrell.github.io/skimpy/ python skimr for Python
library(pins)
library(tidyverse)
library(skimr)
library(arrow)
board <- board_connect()
dat <- pin_read(board, params$pins_name)
meta <- pin_meta(board, params$pins_name)
url_path <- meta$local$url
file_name <- meta$file
object_name <- rev(unlist(str_split(meta$name, "/")))[[1]]
url_download <- paste0(
    str_remove(
        url_path,
        paste0(
            rev(unlist(str_split(url_path, "/")))[2],
            "/")),
    file_name)
```

There are __`r prettyNum(nrow(dat), big.mark = ",", scientific = FALSE)` rows__ and __`r ncol(dat)` columns__. The data source[^1] is used to create our data that is stored in our [pins table](`r meta$local$url`). You can access this pin from a connection to [posit.byui.edu](https://posit.byui.edu) using ``r params$pins_name``.

This data is available to __`r params$available`__.

### Variable description

- __CLA:__ Conjugated linoleic acid in milk fat (percent)
- __Treatment:__ Subject group (SAFF: diet supplemented with safflower oil, MON: diet supplemented with monensin, SAFF/M: diet supplemented with both safflower oil and monensin, Control: control group)

### Variable summary

```{r}
#| echo: false
#| warning: false
skim(dat) |> yank("numeric")
```


```{r}
#| echo: false
#| warning: false
skim(dat) |> yank("character")
```

```{r}
#| echo: true
#| eval: false
#| code-fold: true
#| code-summary: Explore generating code using R
#| code-line-numbers: true
#| file: ../../../data_scripts/conjugated_linoleic_acid.R
```

<!-- ```{python}
#| echo: true
#| eval: false
#| code-fold: true
#| code-summary: Explore generating code using Python
#| code-line-numbers: true
#| file: ../../../data_scripts/YOURFILEPATH
``` -->


## Access data

This data is available to __`r params$available`__.

__Direct Download:__ [`r file_name`](`r url_download`)

#### __R and Python Download:__

##### __URL Connections:__

For public data, any user can connect and read the data using `pins::board_connect_url()` in R.

```r
library(pins)
url_data <- "https://posit.byui.edu/data/`r object_name`/"
board_url <- board_connect_url(c("dat" = url_data))
dat <- pin_read(board_url, "dat")
```

Use this custom function in Python to have the data in a Pandas DataFrame.

```python
import pandas as pd
import requests
from io import BytesIO

def read_url_pin(name):
  url = "https://posit.byui.edu/data/" + name + "/" + name + ".parquet"
  response = requests.get(url)
  if response.status_code == 200:
    parquet_content = BytesIO(response.content)
    pandas_dataframe = pd.read_parquet(parquet_content)
    return pandas_dataframe
  else:
    print(f"Failed to retrieve data. Status code: {response.status_code}")
    return None

# Example usage:
pandas_df = read_url_pin("`r object_name`")
```

#### __Authenticated Connection:__

Our connect server is [https://posit.byui.edu](https://posit.byui.edu/connect/#/content/listing?filter=min_role:viewer&filter=content_type:all&view_type=compact) which you assign to your `CONNECT_SERVER` environment variable. You must [create an API key](https://docs.posit.co/connect/user/api-keys/#api-keys-creating) and store it in your environment under `CONNECT_API_KEY`. 

_Read more about [environment variables and the pins package](../../environment.qmd) to understand how these environment variables are stored and accessed in R and Python with pins._

```r
library(pins)
board <- board_connect(auth = "auto")
dat <- pin_read(board, "`r params$pins_name`")
```


```python
import os
from pins import board_rsconnect
from dotenv import load_dotenv
load_dotenv()
API_KEY = os.getenv('CONNECT_API_KEY')
SERVER = os.getenv('CONNECT_SERVER')

board = board_rsconnect(server_url=SERVER, api_key=API_KEY)
dat = board.pin_read("`r params$pins_name`")
```

[^1]: [`r params$source`](`r params$source`)